### 2013-09-18 chi2014/related.tex

In the realm of crowd-based brainstorming, there are a number of ways this process could be realized. The most basic configuration mirrors that of nominal brainstorming, where individuals brainstorm ideas in isolation of one another, and the resulting ideas are passed on to the requestor (the individual posting the brainstorming task). More sophisticated brainstorming environments are possible, such as those that provide awareness of ideas that others have generated, or those that rely on the crowd to organize or rank the ideas produced by others. In this paper, we focus on the most basic setup, where individuals brainstorm in isolation of one another.

While we are unaware of specific studies of brainstorming processes in crowd marketplaces, there is a range of related research examining more creative processes in this environment. For example, Yu and Nickerson created a system in which individuals participate in an evolutionary algorithm to generate creative chair designs \cite{yu_cooks_2011}. Compared to ideas produced by single individuals, they found the ideas produced as a result of their genetic algorithm were more creative. However, individuals produced only one idea each, compared to the many ideas typically produced by individuals in a brainstorming session. Thus, while their approach demonstrates the creative potential of the crowd, their results say little about brainstorming processes by crowds.

TODO: More crowdsourcing related work here. Maybe the Little iterative vs parallel paper? It includes creative tasks. Perhaps describe some of the unique characteristics of microtask marketplaces, like people's desire to perform a task and move on...

>>>>

In the realm of crowd-based brainstorming, there are a number of ways this process could be realized. The most basic configuration mirrors that of nominal brainstorming, where individuals brainstorm ideas in isolation of one another, and the resulting ideas are passed on to the requestor (the individual posting the brainstorming task). More sophisticated brainstorming environments are possible, such as those that provide awareness of ideas that others have generated, or those that rely on the crowd to organize or rank the ideas produced by others. Examples for these environments are platforms for generating social innovation ideas or product concepts like OpenIDEO, Quirky and Threadless that employ structured process where participants take on different responsibility from generating ideas to evaluating others' ideas. In this paper, we focus on the most basic setup, where individuals brainstorm in isolation of one another.

While we are unaware of specific studies of brainstorming processes in crowd marketplaces, there is a range of related research examining more creative processes in this environment \cite{lewis2011affective, kittur2011crowdforge, Zhang:2012:HCT:2207676.2207708}. For example, Yu and Nickerson created a system in which individuals participate in an evolutionary algorithm to generate creative chair designs \cite{yu_cooks_2011}. Compared to ideas produced by single individuals, they found the ideas produced as a result of their genetic algorithm were more creative. However, individuals produced only one idea each, compared to the many ideas typically produced by individuals in a brainstorming session. Thus, while their approach demonstrates the creative potential of the crowd, their results say little about brainstorming processes by crowds.

Little et el. compared the iterative and parallel human computation processes on a brainstorming task for names for fabricated companies \cite{little2010exploring}. In the iterative condition, participants saw all names suggested by previous participants. Participants in the parallel condition worked in isolation without seeing other participants' ideas. Subjective ratings of the quality of ideas reveal that while the ideas from the iterative condition were rated higher on average, the best ideas from the parallel condition have higher scores than the best ideas from the iterative conditions. The parallel process is more likely to generate names with high ratings, advocating the case for nominal brainstorming over traditional electronic brainstorming. However, the study did not mention categorization of generated ideas, an important measure on flexibility of idea generation \cite{lewis2011affective, nijstad_how_2006, finke1992creative, shah2003metrics}. Each participant also generated only five ideas, leaving the number of ideas requested per participant an open dimension to be explored.

%The nature of microtask marketplace also re.. .. identified high variance of turk eff

%In this paper, we focus on crowd-based brainstorming. While brainstorming has been an implicit component of many creative endeavors in microtask marketplaces, we are unaware of any research that specifically describes and models the brainstorming process in this environment. Furthermore, while there is a rich literature describing brainstorming processes of individuals and groups (e.g., \cite{osborn_applied_1957, pinsonneault_electronic_1999, nijstad_how_2006} OTHERS?), microtask marketplaces have qualitative differences. For example, crowd workers exhibit high variance of effort in completing a task \cite{soylent}. Brainstorming participants in a microtask marketplace are paid for their participation and some might be more eager to complete a task as fast as possible to maximize earnings \cite{kittur2008crowdsourcing}. Furthermore, participants in microtask marketplaces cannot be expected to be spatially or temporally co-located. There many open questions about how brainstorming unfolds in this context.

%TODO: More crowdsourcing related work here. Maybe the Little iterative vs parallel paper? It includes creative tasks. Perhaps describe some of the unique characteristics of microtask marketplaces, like people's desire to perform a task and move on...
